A comprehensive framework to capture the arcana of neuroimaging analysis

### 2019-03-20 manuscript/manuscript.tex
touch ups to manuscript and added response to reviewer

% Insert the name of "your journal" with
% \journalname{myjournal}

@@

% Provenanced mentioned here

@@

The data specification of a Study class are defined by providing a
list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}).
The lists are collated with data specifications in any base Study
classes during the creation of the class. Input data to the study are
distinguished from derivatives by using the \emph{FilesetInputSpec}
and \emph{FieldInputSpec} subtypes. However, the distinction between
input and derived data is somewhat blurred, as derivative specification
entries can be
passed input data when the class is instantiated. In addition,
when subclassing a Study class or combining it in a MultiStudy class,
derivative specification entries can be overridden by input
specification entries, and vice-versa.

@@

The framework provided by Arcana should facilitate the development of workflows
that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.
Each pipeline is accompanied by a text description and
a list of citations to describe the techniques it employs.
The extensibility and modularity of workflows in Arcana should encourage
their reuse, and enable communal development of code repositories.
Arcana analyses are interoperable between different
repository and execution environments. In addition, the development of
Banana is planned to closely follow the specification for BIDS
derivatives \citep{gorgolewski_bids_nodate} for interoperability with
other BIDS apps.

>>>>

% Insert the name of "your journal" with
\journalname{Neuroinformatics}

@@

@@

The data specification of a Study class are defined by providing a
list of \emph{FilesetSpec} and \emph{FieldSpec} objects in the
\emph{add\_data\_specs} class attribute (Figure \ref{fig:data_spec}).
The lists are collated with data specifications in any base Study
classes during the creation of the class. Input data to the study are
distinguished from derivatives by using the \emph{FilesetInputSpec}
and \emph{FieldInputSpec} subtypes. However, the distinction between
input and derived data is somewhat blurred, as derivative specification
entries can be passed input data when the class is instantiated. In addition,
when subclassing a Study class or aggregating it in a MultiStudy class,
derivative entries can be overridden by input entries, and vice-versa.

@@

The framework provided by Arcana should aid the development of workflows
that are consistent with the F.A.I.R. guiding principles \citep{wilkinson_fair_2016}.
Each pipeline is accompanied by a text description and
a list of citations to describe the techniques it employs.
The extensibility and modularity of workflows in Arcana should encourage
their reuse, and enable communal development of code repositories.
Arcana analyses are interoperable between different
repository and execution environments. In addition, the development of
Banana is planned to closely follow the specification for BIDS
derivatives \citep{gorgolewski_bids_nodate} for interoperability with
other BIDS apps.
